---
title: "PA_1"
author: "me"
date: "13/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##COURSE PROJECT
1.Code for reading in the dataset and/or processing the data
```{r}
a<-read.csv("C:/Users/Shreyas Bhoyar/Documents/data/activity.csv")
dim(a)
```
2.Histogram of the total number of steps taken each day
```{r}
d<-tapply(a$steps,a$date,FUN=sum,na.rm=TRUE)
hist(d)
```
3.Mean and median number of steps taken each day
```{r}
tapply(a$steps,a$date,FUN=mean,na.rm=TRUE)
tapply(a$steps,a$date,FUN=median,na.rm=TRUE)
```
4.Time series plot of the average number of steps taken
```{r}
s<-tapply(a$steps,a$interval,FUN=mean,na.rm=TRUE)
plot(s,type="l")

```
5.The 5-minute interval that, on average, contains the maximum number of steps
```{r}
which.max(s)
```
6.Code to describe and show a strategy for imputing missing data
```{r}
sum(is.na(a$steps))
a$steps[is.na(a$steps)]<-mean(a$steps,na.rm=TRUE)
```
7.Histogram of the total number of steps taken each day after missing values are imputed
```{r}
d1<-tapply(a$steps,a$date,FUN=sum,na.rm=TRUE)
hist(d1)
tapply(a$steps,a$date,FUN=mean,na.rm=TRUE)
tapply(a$steps,a$date,FUN=median,na.rm=TRUE)
```
8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
library(dplyr)
k<-weekdays(as.Date(a$date))
t<-replace(k,1:12960,"weekday")
t1<-replace(t,12960:17568,"weekend")
k1<-data.frame(a,as.factor(t1))
names(k1)<-c("steps","date","interval","week")
w1<-filter(k1,week=="weekday")
s1<-tapply(w1$steps,w1$interval,FUN=mean,na.rm=TRUE)
plot(s1,type="l")
w2<-filter(k1,week=="weekend")
s2<-tapply(w2$steps,w2$interval,FUN=mean,na.rm=TRUE)
plot(s2,type="l")
```
